\chapter*{\center \Large \vspace{-4.5cm} ABSTRACT}
\addcontentsline{toc}{section}{ABSTRACT}
\markboth{ABSTRACT}{ABSTRACT} 
\noindent

The technical and legal review of infrastructure concession contracts in Peru faces 
critical challenges of efficiency and consistency due to the complexity of the 
documents involved. At \enquote{ProInversión}, the government agency responsible for 
promoting and structuring private investment projects, typical contracts exceed 200 
pages with multiple chapters, annexes, and complex cross-references. Analysis of the 
current process, based on interviews with institutional specialists, indicates that 
manual review requires an average of more than \enquote{320 hours} of work by 
multidisciplinary teams per contract. This process exhibits high variability in 
evaluation criteria, late detection of inconsistencies, and difficulties in maintaining 
complete traceability of decisions.

This work designs, implements, and evaluates a \enquote{multi-agent artificial 
intelligence system} specialized in \enquote{automated auditing of concession 
contracts}, through a \enquote{hybrid architecture} that combines \textit{Large 
Language Models} (LLMs) with hybrid \textit{Retrieval-Augmented Generation} (FAISS, 
BM25, and Cohere Reranker) and \textit{knowledge graphs} (GraphRAG). The system 
deploys three specialized agents in parallel —Jurist, Auditor, and Chronologist— 
powered by Google's \textit{Gemini 2.5 Pro}, coordinated by an orchestrator that 
integrates automatic document segmentation through robust title detection and 
anti-TOC filtering, multilevel indexing with Section, Global Clause, and Local 
indices, dynamic construction of a contractual knowledge graph with up to 477 nodes 
and 617 semantic relations, and inconsistency detection with full traceability down 
to the specific clause and paragraph. The system is deployed in production via 
\textit{Google Cloud Run} with a web interface (\textit{Next.js}) and a conversational 
bot (\textit{Telegram}), accessible at \texttt{contractia.pe}.

Evaluation on the \enquote{A Contract} (324 pages, 41 
sections, 448 clauses) demonstrated a reduction in initial screening time from 
\enquote{320 hours to approximately 1 hour}, detecting \enquote{119 findings} with 
automatic severity classification (57\% high, 33\% medium, 10\% low) and complete 
traceability. A comparative evaluation between \textit{Gemini 2.5 Pro} and 
\textit{Gemini 3.1 Pro Preview} was also conducted, showing that the former offers 
broader coverage (119 versus 67 findings) at 2.3 times the speed, while the latter 
constructs significantly richer knowledge graphs (477 versus 208 nodes), representing 
a key improvement direction for future versions of the system. \\

\noindent \textbf{Keywords:}\\
\noindent AI Agent; Multi-agent Architecture; Contract Auditing; Hybrid RAG; 
GraphRAG; Automatic Indexing; Inconsistency Detection; LLM; Concession Contracts; 
ProInversión.
